Scikit-learn: machine learning without learning the machinery

### 2014-07-01 article.tex
typo
copyedit, esp. the NLP example part

% Introduce and describe the data
Machine learning is about extracting rules from data, most often with the
goal of making decision on new data \cite{elemstatlearn}. As a simple example, we show on
Fig.\,\ref{fig:data} data about wages in the US, from \cite{berndt1991}:
11 features, including wage, number of years of education and of work
experience, on 534 individuals --samples in machine-learning
jargon. 
Code downloading the data to reproduce the figures can be found on
\url{https://github.com/scikit-learn/SigMobile-paper}.
%
This data showcases many of the typical difficulties in machine learning.
Samples are very irregularly distributed, as most individuals
finished studies after high-school. As a result, there are gapping
holes in the 2D plot of education versus work experience, in which any
statistical analysis is extrapolation. The data is very noisy: for a
given education and work experience wages vary widely. This variability
is probably explained by missing factors, such as sector of
activity, but adding them to the analysis creates a more complex picture,
in 3D or more, rather than 2D, with even more gaps.

@@

\paragraph{A simple text-mining example.}
%
Not every dataset comes as a set of numbers. For instance in natural
language processing (NLP), each observation is a text, \emph{i.e.}~a
string, that needs to be transformed into the data matrix expected by
estimators. Typical, features used to build decisions indicate the
presence of certain words, and often their frequencies.
In spam filtering, it can very relevant to extract from a document that
it contains the term \textsf{viagra}, and possibly how many times.
In other NLP problems, such as finding proper names,
events such as ``next token is the Roman numeral'' may be relevant, as in
``J.P. Kennedy III''. A way to capture this information is to count bigrams,
or $n$-grams. Reusing the {\tt transform} API, scikit-learn
provides \emph{feature extraction} objects, that  such
unstructured data into a data matrix. In these situations, the
$\textbf{X}$ matrix is a
matrix of counting statistics. It is full of zeros, in the sens that
often a word is present only in a few documents. For better scalability,
it can be encoded using SciPy's sparse matrices, that many scikit-learn
estimators process efficiently.

On Fig.\,\ref{fig:code} we give an example of fully functioning code to
do sentiment polarity classification for movie reviews: given a review,
it outputs whether the review is positive about the movie it concerns.
The code demonstrates the use of pipelines, and also shows how machine
learning ties into unrelated Python's modules: downloading, unpacking and
learning from a dataset are all done in one programming language.
This script first fetches the hand-labeled movie review dataset from
\cite{pang2004} and unpacks it to disk using standard Python libraries.
It then loads these using scikit-learn data loading functions, makes a
pipeline of a \textsf{tf--idf} feature extractor
\cite{rennie2003tackling} --than turns strings into a sparse matrix based
on word frequencies-- and logistic regression, and finally trains the
model. Parameters for the feature extractor and the LogReg classifier
were set manually.

@@

The greatest asset of the scikit-learn project is its breadth of
contributors, coming from different backgrounds, working in different
institutions, with a variety of applications --more than 200 contributors
total, 15 active core contributors in the past year. Indeed, not only
is there strength in numbers, but also the convergence of points of views
make better code and better design. From a developer's perspective, the
project thus is managed with the goals of enabling newcomers to
contribute while keeping a high quality assurance. For these purposes, we
rely heavily on Github --\url{http://github.com}-- with an online
development workflow relying on distributed version control using git,
and intensive code review. The code review process is a great asset to
raising the quality of the code, from all points of view: algorithmic,
numerical robustness, homogeneity of APIs, ease of use, documentation.
Another central aspect for quality in the project is the heavy use of
unit testing (up to 88\% of the lines of code are covered), run
continuously on all contributions thanks to the travis platform
(\url{http://travis-ci.org}).

>>>>

% Introduce and describe the data
Machine learning is about extracting rules from data, most often with the
goal of making decision on new data \cite{elemstatlearn}. As a simple example, we show on
Fig.\,\ref{fig:data} data about wages in the US, from \cite{berndt1991}:
11 features, including wage, number of years of education and of work
experience, on 534 individuals --samples in machine-learning
jargon. 
Code downloading the data to reproduce the figures can be found on
\url{https://github.com/scikit-learn/SigMobile-paper}.
%
This data showcases many of the typical difficulties in machine learning.
Samples are very irregularly distributed, as most individuals
finished studies after high-school. As a result, there are gaping
holes in the 2D plot of education versus work experience, in which any
statistical analysis is extrapolation. The data is very noisy: for a
given education and work experience wages vary widely. This variability
is probably explained by missing factors, such as sector of
activity, but adding them to the analysis creates a more complex picture,
in 3D or more, rather than 2D, with even more gaps.

@@

\paragraph{A simple text-mining example.}
%
Not every dataset comes as a set of numbers. For instance in natural
language processing (NLP), observations are strings,
which needs to be transformed into the data matrix expected by
estimators. Often, features used to build decisions indicate the
presence of certain words, or their frequencies.
In spam filtering, it can be very relevant to extract from a document that
it contains the term \textsf{viagra}.
In other NLP problems, such as finding proper names,
events such as ``next token is a Roman numeral'' may be relevant, as in
``J.P. Kennedy III''.
Reusing the {\tt transform} API, scikit-learn
provides \emph{feature extraction} objects, that turn such
unstructured data into a data matrix. In these situations, the
$\textbf{X}$ matrix is a matrix of counting statistics.
Since each word is typically present in only a few documents,
the data matrix will be mostly zeros.
SciPy offers a \emph{sparse matrix} package
that stores the zeros in such matrices implicitly,
and many scikit-learn estimators use that package to improve scalability.

On Fig.\,\ref{fig:code} we give an example of fully functioning code to
do sentiment polarity classification for movie reviews: given a review,
it outputs whether the review is positive about the movie it concerns.
The code demonstrates the use of pipelines, and also shows how machine
learning ties into unrelated Python's modules: downloading, unpacking and
learning from a dataset are all done in one programming language.
This script first fetches a hand-labeled movie review dataset
\cite{pang2004} and unpacks it to disk using standard Python libraries.
It then loads these using scikit-learn data loading functions, makes a
pipeline of a \textsf{tf--idf} feature extractor
\cite{rennie2003tackling} --that turns strings into a sparse matrix based
on word frequencies-- and logistic regression, and finally trains the
model. Parameters for the feature extractor and the classifier
were set manually.

@@

The greatest asset of the scikit-learn project is its breadth of
contributors, coming from different backgrounds, working in different
institutions, with a variety of applications --more than 200 contributors
total, 15 active core contributors in the past year. Indeed, not only
is there strength in numbers, but also the convergence of points of views
make better code and better design. From a developer's perspective, the
project thus is managed with the goals of enabling newcomers to
contribute while keeping a high quality assurance. For these purposes, we
rely heavily on Github (\url{http://github.com}) with an online
development workflow relying on distributed version control using git,
and intensive code review. The code review process is a great asset to
raising the quality of the code, from all points of view: algorithmic,
numerical robustness, homogeneity of APIs, ease of use, documentation.
Another central aspect for quality in the project is the heavy use of
unit testing (up to 88\% of the lines of code are covered), run
continuously on all contributions thanks to the travis platform
(\url{http://travis-ci.org}).
